\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}

### 2024-04-10 lin-vs-cen.tex
WTF

\title{\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}}
\author{Prosenjit~Bose, Vida~Dujmović, Hussein~Houdrouge, Mehrnoosh~Javarsineh, and Pat~Morin}

>>>>

\title{\MakeUppercase{Linear versus centred chromatic numbers}\thanks{This research was partly funded by NSERC.}}
\author{Prosenjit~Bose\thanks{School of Computer Science, Carleton University},\quad Vida~Dujmović\thanks{Department of Computer Science and EE, University of Ottawa},\quad Hussein~Houdrouge\footnotemark[2],\quad Mehrnoosh~Javarsineh\footnotemark[2],\quad and Pat~Morin\footnotemark[2]}
